### 2016-09-22 features.tex
Move basic usage to the top of the section, and add an intro paragraph
I feel this is more motivating, to jump in with some usage, before the
detailed listing of features.

% Features to discuss in-depth:

>>>>

% Features to discuss in-depth:
This section gives a basic introduction of SymPy, and lists its features.
A few features---assumptions, simplification, calculus, polynomials, printers,
solvers, and matrices---are core components of SymPy and are discussed in
depth. Many other features are discussed in depth in the supplementary
material.

\subsection{List of Features}
